Using traffic analysis to identify The Second Generation Onion Router

### 2011-02-26 thesis/experiment.tex
Rewriting of some bits of the equipment section

  The network equipment chosen to run the experiment is a simple hub or
  'repeater' which duplicates all packets transmitted on all ports. This makes it
  easy to monitor all communications across the network for analysis purposes
  \parencite{website:hub-reference}.

@@

  VirtualBox provides a virtualization environment that allows guest operating
  systems to run in a virtual environment on a host operating system
  \parencite{:fk}. It supports snapshots and a remote control facility which make
  it useful for running a controlled experiment \parencite{:uq}.

@@

  Ruby is an object orientated, dynamic programming language which is useful for
  rapid prototyping and as such has been used to automate the simulation
  described in this experiment \parencite{:2010uq}. It is supported by the
  Selenium framework and so can be used to automate a web browser and includes
  community developed plug-in modules called gems that provide functionality for
  monitoring automated software and performing test sequences.

@@

  The Ubuntu Linux operating system is freely available Linux operating system
  available for desktop personal computers \parencite{:2010ly}. It comes
  packaged with the 'tcpdump' software and can be configured in a reliable and
  consistent way with typical set of POSIX tools and the 'apt-get' package
  manager. \parencite{Pereira:2011uq}.

@@

  Selenium is a web testing framework which allows automated testing of web pages
  through any Javascript enabled web browser \parencite{:2010ys}. A web browser
  can be controlled remotely using the Selenium Remote Control Server component,
  which in turn can be controlled with a number of programming languages including
  Ruby. This experiment makes use of a number of selenium scripts which
  approximate user interactions with a website which trigger network traffic.

@@

  OpenSSH is a freely available suite of connectivity tools
  \parencite{:2010zr,:ve} that supports remote command execution
  \parencite{Tucker:2010ly, :2010zr}.

@@

  The Apache web server is the most prevalent web server used on the internet
  \parencite{2010:dq}. Details about apache go here \parencite{:qf}.

@@

  Sinatra is a simple framework for creating dynamic web applications using the
  Ruby programming language \parencite{:2010bh}.

@@

Four identical IBM desktop computer systems were prepared and arranged as shown
in figure \ref{physical-setup}.

>>>>

  Most modern network appliances used for routing, even those labelled as hubs,
  include switching capabilities, which means that packets routed are only
  delivered to the addressed host. This makes eavesdropping difficult. For
  the purpose of this experiment a simple hub or repeater is required. A hub
  does not examine packet delivery information, it simple broadcasts all packets
  received to every connected port, allowing for passive eavesdropping without
  complicated network configuration \parencite{website:hub-reference}.

@@

  VirtualBox software allows multiple guest operating systems to run in an
  isolated virtual environment on a host operating system \parencite{:fk}.
  It is free software and supports both snapshots and a remote control facility
  which make it useful for running a controlled experiment \parencite{:uq}.

@@

  Ruby is an object orientated, dynamic programming language which is useful for
  rapid prototyping and is supported by a large community that has developed
  powerful add on software in the form of Ruby Gems \parencite{:2010uq}. These
  Gems include support for the Selenium browser testing framework, process
  monitoring, dynamic web content generation and automated testing.

@@

  The Ubuntu Linux operating system is freely available Linux operating system
  available for desktop personal computers \parencite{:2010ly}. It comes
  packaged with the 'tcpdump' software and can be configured in a reliable and
  consistent way with typical set of POSIX tools and the 'apt-get' package
  manager \parencite{Pereira:2011uq}.

@@

  Selenium is a web testing framework which allows automated testing of web pages
  through any Javascript enabled web browser \parencite{:2010ys}. A web browser
  can be controlled remotely using the Selenium Remote Control Server component,
  which in turn can be controlled with a number of programming languages including
  Ruby. Using Selenium the typical interactions a user makes when viewing a
  website can be simulated.

@@

  OpenSSH is a freely available suite of connectivity tools
  \parencite{:2010zr,:ve} that supports remote command execution
  \parencite{Tucker:2010ly, :2010zr}. The client component of OpenSSH is
  installed by default on the Ubuntu operating system and the server component
  is easily installed using the apt-get package management system.

@@

  The Apache web server is the most prevalent web server used on the Internet
  \parencite{2010:dq}. The Apache web server can serve static web content over
  both the HTTP and HTTPS protocols \parencite{Foundation:2011uq}. Combined with
  software such as Sinatra it can serve dynamic web content.

@@

  Sinatra is a simple framework for creating dynamic web applications using the
  Ruby programming language \parencite{:2010bh}. Sinatra requires very little
  configuration and development time to develop dynamic web applications.

@@

Four identical desktop computer systems were prepared and arranged as shown
in figure \ref{physical-setup}.
